### 2020-06-27 docs/LaTex/Paper.tex
Completes docs and adds a first version for a python GUI

Another important consideration inside TTN platform is to check which decoder is chosen for the received payloads, this can be checked by clicking on \cmd{Payload Formats} tab inside Application Overview. As can be seen in figure \ref{fig:CayenneLPP_decoder}, it is so importan to choose the \cmd{CayenneLPP} decoder, because as indicated, the payload is being encoded in the end-nodes using the CayenneLPP standard.

@@

\begin{itemize}
  \item In a first place the reader will need to create a new device for the \textbf{IoTagent-LoRaWAN}, this
\end{itemize}

>>>>

Another important consideration inside TTN platform is to check which decoder is chosen for the received payloads, this can be checked by clicking on \cmd{Payload Formats} tab inside Application Overview. As can be seen in figure \ref{fig:CayenneLPP_decoder}, it is so importan to choose the \cmd{CayenneLPP} decoder, because as indicated, \myuline{the payload is being encoded in the end-nodes using the CayenneLPP standard}.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=.9\textwidth]{../pictures/docker_containers_deployed.png}  
  \caption{\cmd{tmux} showing docker containers status and logs.}
  \label{fig:docker_containers}
\end{figure}

So cloning the project and navigating to \cmd{src/fiware/} folder in the terminal the reader will must perform \cmd{docker-compose up -d} to deploy all containers and keep detached from the logs output. Once this has been done, performing \cmd{docker ps -a} will show the status of deployed containers, as figure \ref{fig:docker_containers} shows. In a similar way, to check the logs the reader could perform \cmd{docker-compose logs -f <NAME>} where the argument \cmd{<NAME>} is optional and when is not provided \cmd{docker-compose} will show logs for all containers; this is also shown in picture \ref{fig:docker_containers}.

When these containers are properly deployed, it should be possible to send the HTTP requests, however, these must follow a precise order;

\begin{itemize}
  \item In a first place the reader will need to create a new device for the \textbf{IoTagent-LoRaWAN}, this can be done performing a \cmd{POST} HTTP request whose body will include the necessary data to retrieve the TTN stack context data.

  \begin{lstlisting}[%
    % float=ht,
    language=json,
    firstnumber=1,
    caption={Device provisioning for IoTagent-LoRaWAN},
    label=ej:provisioning_devices
    ]
    curl localhost:4061/iot/devices -s -S -H 'Content-Type: application/json' -H 'Accept: application/json' -H 'fiware-service: atosioe' -H 'fiware-servicepath: /lorattn' -d @- <<EOF
    {
      "devices": [
        {
          "device_id": "node_2",
          "entity_name": "LORA-N-2",
          "entity_type": "LoraDevice",
          "timezone": "Europe/Madrid",
          "attributes": [
            {
              "object_id": "analog_in_1",
              "name": "analog_in_1",
              "type": "Number"
            }
          ],
          "internal_attributes": {
            "lorawan": {
              "application_server": {
                "host": "eu.thethings.network",
                "username": "dendrometer",
                "password": "ttn-account-v2.173lH8wwDiIRC8E2JgM9ScXyuNRlPpMefpazS0TIhnU",
                "provider": "TTN"
              },
              "dev_eui": "00EC51D264A6F8FD",
              "app_eui": "70B3D57ED0030B5D",
              "application_id": "dendrometer",
              "application_key": "3736B21218C4443F639FAF4114B723A1"
            }
          }
        }
      ]
    }
    EOF

    EOF
  \end{lstlisting}
\end{itemize}
